A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-10-11 sections/04-research-design.tex
Add sentence on CUDA and OpenMPI.
Expliciting ethical approval

The course presents students with a series of software engineering challenges
in the form of assignments. The final is composed of an essay and a
presentation on a relevant topic related to Concurrent, Parallel and
Distributed Computing.  The course material is available
online~\footnote{\url{https://phrb.github.io/MAC5742-0219} [Accessed in
07/08/2017]}.

@@

We obtained responses, and consent to use them in our research, from 38 of the
54 students enrolled in the Concurrent, Parallel and Distributed Computing
course. Section \ref{sec:responses} presents a detailed description of
each set of questions and our analysis of the students' responses.

>>>>

The course presents students with a series of software engineering challenges
in the form of assignments involving GPU programming with CUDA and distributed
computing with OpenMPI. The final is composed of an essay and a presentation on
a relevant topic related to Concurrent, Parallel and Distributed Computing.
The course material is available
online~\footnote{\url{https://phrb.github.io/MAC5742-0219} [Accessed in
07/08/2017]}.

@@

We obtained the ethical approval from the Department of Computer Science at the
University of São Paulo to conduct this study based on the questionnaire. We
collected responses, and consent to use them in our research, from 38 of the 54
students enrolled in the Concurrent, Parallel and Distributed Computing course.
Section \ref{sec:responses} presents a detailed description of each set of
questions and our analysis of the students' responses.
